\begin{multicols}{2}
    \begin{itemize}
        \item [1.]adhere v. 黏附(=stick)
        

        (adhered-adhered)


        adhere to sth 坚持，遵守
        \item [2.]tumble v.\&n. 摔倒、翻滚
        

        tumble dryer 滚筒式烘干机
        \item [3.]overlook v. 俯视，忽略
        \item [4.]glamorous adj. 吸引人的
        \item [5.]deposit n. 订金，押金，存款
        \item [6.]mandatory adj. 必须的，法律要求的
        \item [7.]tenant n. 房客，租户
        \item [8.]baffle v. 使困惑
        
        e.g.His behavior baffles me.
        \item [9.]detrimental adj. 有害的
        \item [10.]incentive n. 激励，鼓励
        
        tax incentives to encourage savings\quad 鼓励储蓄的税收措施
        \item [11.]suppress v. 抑制，镇压，禁止
        \item [12.]ethic n. 道德
        \item [13.]infer v. 推断，暗示
        \item [14.]hypocrisy n. /\textipa{hI'pA:kr@si}/
        
        伪善，虚伪
        \item [15.]hypocritical adj. 虚伪的，伪善的
        \item [16.]tactic n. 方法、战术
        \item [17.]outright adj.\&adv. 完全彻底的；公开直接的
        \item [18.]concede v. 承认
        \item [19.]notwithstanding prep.\&adv. 尽管
        \item [20.]scrutiny n. 仔细审查
        \item [21.]scrutinize v. 仔细审查
        \item [22.]recollection n. 记忆，回忆
        \item [23.]complementary adj. 互补的
        \item [24.]speak of 谈及
        \item [25.]responsive adj. 反应积极的；热情的
        
        be responsive to 对...做出积极反应；对...热情
        \item [26.]susceptible adj. 易受...影响(或伤害)；多愁善感的
        
        be susceptible to... 容易受...影响
        

        be susceptible of... 可以...的


        e.g.1:He's highly susceptible to flattery.他爱听恭维话


        e.g.2:She was both charming and susceptible.她迷人而多情


        e.g.3:Is this situation not susceptible of improvement by legislation?
        这种状况不能通过立法加以改善吗？
        \item [27.]alliance n. 联盟、同盟
        

        alliance between A and B
        \item [28.]undercurrent n. 潜在的情绪(尤指负面)
        \item [29.]permeate v. (气体、液体)渗透、弥漫；(思想、影响)感染、传播
        \item [30.]dissimilar adj. 不同的
        \item [31.]apt adj. 恰当的；有...倾向的
        

        be apt to do 容易...
        \item [32.]precedence n. 优先；优先权
        

        take (sharper) precedence over 比...更重要


        in order of precedence 按照重要次序排列


        e.g.Dating and relationships with boys take sharper precedence over sisterhood.
        和男生的关系比姐妹关系更重要
        \item [33.]dilute v. 冲淡、稀释、削弱
        \item [34.]dubious adj. 怀疑，可疑的，不一定的
        
        be dubious about... 对...怀疑
        \item [35.]indigenous adj. 本地的
        
        (=native)
        \item [36.]specimen n. 样品，样本
        \item [37.]refuge n. 庇护；避难所
        
        take/seek refuge from... 寻求庇护躲\dots
        \item [38.]expire v. 到期；去世
        
        sth expire ... 到期/去世
        \item [39.]deplete v. 大量减少(usually passive)
        
        Food supplies were severely depleted.食物供应已严重不足
        \item [40.]legislature n. 立法机构
        \item [41.]bill n. 议案、法案
        \item [42.]monolingual adj. 只使用一种语言的
        
        bilingual adj. 会两种语言的
        \item [43.]immersive adj. 沉浸式的、身临其境的
        \item [44.]ethnicity n. the state or fact of 
        belonging to a particular ethic group
        \item [45.]lag v. 落后
        
        lag behind... 落后于\dots
    \end{itemize}
\end{multicols}