Directions: For this part, you are allowed 30 minutes to write an essay that begins with the sentence 
“Nowadays parents are increasingly aware that allowing kids more freedom to explore and learn on their own helps foster their independence and boost their confidence.” 
You can make comments, cite examples or use your personal experiences to develop your essay. 
You should write at least 150 words but no more than 200 words not including the sentence given.
~\\


主体：父母，家庭教育
~\\


家长给自由：角色：
~\\


Nowadays parents are increasingly aware that allowing kids more freedom to explore and learn on their own 
helps foster their independence and boost their confidence. 


The understanding, however, leads to a widely debated topic: to what extent should children be given freedom. 
While the question cannot be answered with precise numbers, it highlights the need to define the role of parents in their children’s journey of exploration and learning.(把抽象的变具体)


True freedom for children involves providing opportunities for exploration within a framework of guidance and safety, rather than unchecked liberty.
(放肆的自由). (上一句笼统概括、下定义，下一句写具体的例子，要注意把每一个抽象的要素转化为具体的东西)
People should create an environment where children can pursue their interests, make decisions and… 
with the understanding that boundaries and support are readily available when needed.


The role of the parent is thus not diminished but transformed into that of a mentor who guides, advises and supports.
(下定义：…不是…，而是超越了…)父母不应该只教孩子使用电子产品，而更应该教如何培养数字时代的素养、批判性思维等


In conclusion, providing children with the freedom to explore and … is a adj. art that requires parents to …(后面补充要注意的点) 
It’s about creating a secure foundation on which children can build as they stretch their wings. In the words of Maria Montessori, 
“The greatest gifts we can give our children are the roots of responsibility and the wings of independence.” (纠正青少年观念)


蒙氏教育