Directions: For this part, you are allowed 30 minutes to write an essay that begins with the sentence "Today more and more people begin to realize the pleasures and joys of real-world social interaction." 
You can make comments, cite examples or use your personal experiences to develop your essay. You should write at least 150 words but no more than 200 words. 
~\\


Today more and more people begin to realize the pleasures and joys of real-world social interaction. 
(通过问题引起下文) In an age where technological 
advancements promise to shrink the world and 
bring us closer, \textbf{a paradoxical scenario}(插入比喻) 
unfolds: (具体讲什么变远，什么变近)(\textbf{具体})the more 
connected we are by technology, the wider the 
emotional and psychological gaps between us 
seem to grow. This contradiction hints at 
(hint v. 暗示  hint at sth)
a truth: 现实更重要


(拿网恋做反例)


The reason is simple: the emotional impact of 
physically being with someone and the unspoken 
understanding(心照不宣的默契) that comes from a 
glance or a touch cannot be replicated
(replicate v. 复制\quad 无法被替代：cannot be replicated)
 by digital means. (人际交往都可以用)Many relationships start 
 with texts and virtual chats, where emotions 
 and sentiments are exchanged through screens. 
 Yet, no matter how intense these digital 
 exchanges might be, they \textbf{pale}(v. 苍白、逊色) 
 in comparison to the moment when two people 
 hold hands for the first time.(\textbf{when
..., everything else pales in comparison}) 
Similarly, during disagreements that inevitably 
arise in any relationship, a single real-life 
hug can \textbf{melt} away misunderstanding, 
which is feat that countless online apologies 
might fail to achieve.


(先批驳，然后揭露本质)Realizing the pleasures 
and joys of real-world social interaction 
teaches us a lesson(网恋这个例子只是工具) about 
human nature. (转换的同时对上文总结)It 
underscores(v. 突出) our need for genuine 
connections that go beyond digital communications. 
These interactions, with all the imperfections, 
allow us to feel deeply, understand profoundly 
and connect on a level that digital platforms 
can never fully accomodate.


The words of \textbf{Maya Angelou} resonate(v. 产生共鸣) 
deeply: \textbf{ ``People will forget what you said, 
people will forget what you did, but people 
will never forget how you made them 
feel." }(表白金句) It's the pleasures and joys 
of real-world social interaction that truly 
affirms our existence of empathy, connection 
and love.